### 2019-04-05 README.Rmd
Tweaks to various docs

```{r setup, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

@@

```{r authors, echo = FALSE, results = 'asis'}

unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>%
  purrr::keep(~"aut" %in% .$role) %>%
  purrr::map_chr(~paste(.$given, .$family)) %>%
  glue::glue_collapse(sep = ", ", last = " and ") %>%
  paste0("Authors: _", ., "_") %>%
  cat()
```

@@

**citesdb** is an R package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 20 million records of reported shipments of wildlife and wildlife products subject to oversight under the [Convention on International Trade in Endangered Species of Wild Fauna and Flora](https://www.cites.org).

@@

```{r install_me, eval = FALSE}

source("https://install-github.me/ecohealthalliance/citesdb")
```

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}

options(width = 120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r getdata, include = FALSE}

if (!citesdb::cites_status()) citesdb::cites_db_download()
```

```{r, warning = FALSE}

library(citesdb)
library(dplyr)

@@

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}

citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r, results = "asis", echo = FALSE}

print(citation("citesdb"), style = "textVersion")
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

@@

```{r authors, echo = FALSE, results = 'asis'}
unclass(desc::desc_get_authors(here::here("DESCRIPTION"))) %>%
  purrr::keep(~"aut" %in% .$role) %>%
  purrr::map_chr(~paste(.$given, .$family)) %>%
  glue::glue_collapse(sep = ", ", last = " and ") %>%
  paste0("Authors: _", ., "_") %>%
  cat()
```

@@

**citesdb** is an R package to conveniently analyze the full CITES shipment-level wildlife trade database, available at <https://trade.cites.org/>. This data consists of over 40 years and 20 million records of reported shipments of wildlife and wildlife products subject to oversight under the [Convention on International Trade in Endangered Species of Wild Fauna and Flora](https://www.cites.org).

@@

```{r install_me, eval = FALSE}
source("https://install-github.me/ecohealthalliance/citesdb")
```

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
options(width = 120)
knitr::opts_chunk$set(cache = TRUE)
citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r getdata, include = FALSE}
if (!citesdb::cites_status()) citesdb::cites_db_download()
```

```{r, warning = FALSE}
library(citesdb)
library(dplyr)

@@

```{r message = FALSE, warning = FALSE, error = FALSE, include = FALSE}
citesdb::cites_disconnect()
MonetDBLite::monetdblite_shutdown()
```

@@

```{r, results = "asis", echo = FALSE}
print(citation("citesdb"), style = "textVersion")
```
